Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-10-04 manuscript/supplemental_material.Rnw
plot too short vs read length

\begin{figure}
<<reads.vs.read.length,fig.width=8,fig.height=8,echo=FALSE>>=
print(ggplot(star.logs.wide,
             aes(x=as.numeric(input.read.length),
                 y=as.numeric(input.reads),
                 color=capfirst(species),
                 shape=capfirst(species)
                 ))
      + scale_shape_manual(values=1:nlevels(as.factor(star.logs.wide[,species])),
                           guide=guide_legend(title="Species")
                           )
      + scale_color_discrete(guide=guide_legend(title="Species")
                             )
      + geom_point(size=5)
      + xlab("Trimmed Read Length")
      + ylab("Read number")
      + scale_y_log10()
      + theme(legend.text=element_text(face="italic")
              )
      )
@ 
\caption{RNA Read number as a function of trimmed read length}
\label{fig:transcriptome_reads_vs_read_length}
\end{figure}

>>>>

\begin{figure}
<<reads.vs.read.length,fig.width=8,fig.height=6,echo=FALSE>>=
grid::pushViewport(grid::viewport(layout=grid::grid.layout(ncol=2,nrow=1,widths=c(1,1.4))))
print(ggplot(star.logs.wide,
             aes(x=as.numeric(input.read.length),
                 y=as.numeric(input.reads),
                 color=capfirst(species),
                 shape=capfirst(species)
                 ))
      + scale_shape_manual(values=1:nlevels(as.factor(star.logs.wide[,species])),
                           guide=guide_legend(title="Species")
                           )
      + scale_color_discrete(guide=guide_legend(title="Species")
                             )
      + geom_point(size=5)
      + xlab("Trimmed Read Length")
      + ylab("Number of input reads")
      + scale_y_log10()
      + theme(legend.position="none"
              ),
      vp=grid::viewport(layout.pos.row=1,layout.pos.col=1)
      )
print(ggplot(star.logs.wide,
             aes(x=as.numeric(input.read.length),
                 y=as.numeric(`% of reads unmapped: too short`)#,
                 # color=capfirst(species),
                 # shape=capfirst(species)
                 ))
      + scale_shape_manual(values=1:nlevels(as.factor(star.logs.wide[,species])),
                           guide=guide_legend(title="Species")
                           )
      + scale_color_discrete(guide=guide_legend(title="Species")
                             )
      + geom_point(aes(color=capfirst(species),shape=capfirst(species)),size=5)
      + stat_smooth(method="lm")
      + xlab("Trimmed Read Length")
      + ylab("Unmapped Too Short %")
      + theme(legend.text=element_text(face="italic"),
              legend.position="right"
              ),
            vp=grid::viewport(layout.pos.row=1,layout.pos.col=2)
      )
grid::popViewport()
@ 
\caption{RNA Read number as a function of trimmed read length}
\label{fig:transcriptome_reads_vs_read_length}
\end{figure}
